RDDtools: an R package for Regression Discontinuity Design
========================================================

**RDDtools** is a new R package under development, designed to offer a set of tools to run all the steps required for a Regression Discontinuity Design (RDD) Analysis, from primary data visualisation to discontinuity estimation, sensitivity and placebo testing. 


Installing **RDDtools**
-----------------------

This github website hosts the source code. One of the easiest ways to install the package from github is by using the R package **devtools**:

```{r eval=FALSE}
library(devtools)
install_github(repo="RDDtools", username="MatthieuStigler", subdir="RDDtools")
```

Note however the latest version of RDDtools only works with R 3.0, and that you might need to install  [Rtools](http://stat.ethz.ch/CRAN/bin/windows/Rtools/) if on Windows. 


Documentation
-----------------------
The (preliminary documentation) is available in the help files directly, as well as in the *vignette*. The vignette can be accessed from R with vignette("RDDtools"), or by accessing the [pdf](https://github.com/MatthieuStigler/RDDtools/raw/master/RDDtools/inst/doc/RDDtools.pdf) stored on this github. 

Using RDDtools: a quick example
-----------------------

**RDDtools** works in an object-oriented way: the user has to define once the characteristic of the data, creating a *RDDdata* object, on which different anaylsis tools can be applied, such as:
+  Simple visualisation of the data using binned-plot: **plot()**
+  RDD parametric estimation: **RDDreg_lm()**
+  RDD local non-parametric estimation: **RDDreg_np()**
+  Plot of sensitivity to bandwidth: **plotSensi()**
+  Placebo plot using different cutpoints: **plotPlacebo()**


Load the package, and load the built-in dataset from [Lee 2008]:

```{r options, echo=FALSE}
opts_chunk$set(warning= FALSE, message=FALSE, fig.align="center", fig.path='figuresREADME/')
```


```{r}
library(RDDtools)
data(Lee2008)
```

Declare the data as a RDDdata object:

```{r}
Lee2008_rdd <- RDDdata(y=Lee2008$y, x=Lee2008$x, cutpoint=0)
```


You can now directly summarise and visualise this data:

```{r dataPlot}
summary(Lee2008_rdd)
plot(Lee2008_rdd)
```


As well as run a simple local regression, using the [Imbens and Kalyanaraman 2012] bandwidth:
```{r RegPlot}
bw_ik <- RDDbw_IK(Lee2008_rdd)
reg_nonpara <- RDDreg_np(RDDobject=Lee2008_rdd, bw=bw_ik)
print(reg_nonpara)
plot(x=reg_nonpara)

```


One can easily check the sensitivity of the estimate to different bandwidths:
```{r SensiPlot}
plotSensi(reg_nonpara, from=0.05)
```


  [Imbens and Kalyanaraman 2012]: http://ideas.repec.org/a/oup/restud/v79y2012i3p933-959.html "Imbens, G. & Kalyanaraman, K. (2012) Optimal Bandwidth Choice for the Regression Discontinuity Estimator, Review of Economic Studies, 79, 933-959"
  
  [Lee 2008]: http://ideas.repec.org/a/eee/econom/v142y2008i2p675-697.html "Lee, D. S. (2008) Randomized experiments from non-random selection in U.S. House elections, Journal of Econometrics, 142, 675-697"
  
  